---
title: "ENVS-193DS_homework_03"
format: html
---

Link to github repository: 
https://github.com/oregel714/ENVS-193DS_homework-03.git
```{r}
messages = FALSE
# reading in necessary packages 

library(tidyverse)
library(here)
library(gt)
library(flextable)
library(janitor)
library(readxl)

# reading in data 
ActiveData1 <- read_csv("DataSheet(1).csv")


```


```{r}

money_spent_long_day <- ActiveData1 |> 
  select(`Long Day`, `Money Spent`) |> 

average_money_summary <- money_spent_long_day |> 
  group_by(`Long Day`) |> 
  summarize(mean = mean(`Money Spent`),
            sd = sd(`Money Spent`),
            se = sd / sqrt(n()),
            ci_lower = mean - qt(0.975, df = n() - 1) * se,
            ci_upper = mean + qt(0.975, df = n() - 1) * se) |> 
  mutate(across(c(mean, sd, se, ci_lower, ci_upper),
                ~ round(.x, 1)))

average_money_summary |> 
  gt() |> 
  cols_label(
    `Long Day` = "Long Day",
    mean = "Mean",
    sd = "Standard Deviation",
    se = "Standard Error",
    ci_lower = "95% Confidence Level (Lower)",
    ci_upper = "95% Confidence Level (Upper)"
    
  ) |> 
  tab_header(title = "Money Spent Summary Statistics")



```

Problem #1: 

I can summarize my data by comparing two groups (long day vs. non-long day) and the average amount of money spent depending on the day. On long days, I'm on campus for more than 5 hours and I feel that I am more tempted to spend money on campus the longer I am here. I can also compare the observations of mean dollars spent on campus between the days that I had breakfast or not. This would allow me to observe if having breakfast might influence whether or not I spend money on campus. 

```{r}
# wrangling and cleaning data

clean_names(ActiveData1)

ggplot(data = ActiveData1,
       aes(x = `Long Day`,
           y = `Money Spent`,
           color = `Money Spent`)) + 
  geom_boxplot()
  geom_jitter(width = 0.1)


```

```{r}
avg_money <- ActiveData1 |> 
  filter(`Long Day` == "Yes") |> 
  summarize(mean_money_yes = mean(`Money Spent`))

avg_money2 <- ActiveData1 |> 
  filter(`Long Day` == "No") |> 
  summarize(mean_money_no = mean(`Money Spent`))




```

